### 2024-10-25 MetadataS1/MetadataS1.tex
version submitted to ecology - Data paper

\begingroup  
  \centering
\textbf{Long-term abundance time-series of the High Arctic terrestrial vertebrate community of Bylot Island, Nunavut}\\[1.5em]
 Louis Moisan\textsuperscript{1,2}, Azenor Bideault\textsuperscript{2,3}, Gilles Gauthier\textsuperscript{4}, Éliane Duchesne\textsuperscript{1}, 
 Dominique Fauteux\textsuperscript{5}, Dominique Berteaux\textsuperscript{1}, Pierre Legagneux\textsuperscript{3,6}, Marie-Christine Cadieux \textsuperscript{3} and Joël Bêty\textsuperscript{1}\\[1.5em]
\textbf{Author Affiliations}:\\
\textsuperscript{1} Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Chimie et Géographie, Université du Québec à Rimouski, Rimouski, QC, Canada\\
\textsuperscript{2} Chaire de Recherche du Canada en Écologie Intégrative, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Université de Sherbrooke, Sherbrooke, QC, Canada\\
\textsuperscript{3} Chaire de Recherche Sentinelle Nord sur l’Impact des Migrations Animales sur les Écosystèmes Nordiques, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Université Laval, Québec, QC, Canada\\
\textsuperscript{4} Centre d’Études Nordiques, Département de Biologie, Université Laval, Québec, QC, Canada\\
\textsuperscript{5} Centre d’Études Nordiques, Centre de Connaissance et d’Exploration de l’Arctique, Musée Canadien de la Nature, Ottawa, ON, Canada\\
\textsuperscript{6} Centre d’Études Biologiques de Chizé (CEBC-CNRS), Université de La Rochelle, France 
\\[1.5em]
\textbf{Corresponding Author}:\\
\textit{\href{mailto:louis.moisan.bio@gmail.com}{louis.moisan.bio@gmail.com}}\\
\textit{\href{mailto:joel_bety@uqar.ca}{joel{\textunderscore}bety@uqar.ca}}
\\[1.5em]
\textbf{Open Research statement}:\\
The data set is publicly available at \url{https://datadryad.org/XXXXXXX} and the raw data and codes used to extract the data set are publicly available at \url{https://zenodo.org/XXXXXXXXXX}.\\
\endgroup
\newpage

@@

    \section*{C. Data set description}
                \subsection*{1. Originators}
                \textbf{Gilles Gauthier}, Centre d’Études Nordiques, Département de Biologie, Université Laval, Québec, QC, Canada\\
                \textbf{Joël Bêty},  Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Chimie et Géographie, Université du Québec à Rimouski, Rimouski, QC, Canada \\
                \textbf{Pierre Legagneux}, Chaire de Recherche Sentinelle Nord sur l’Impact des Migrations Animales sur les Écosystèmes Nordiques, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Centre d’Études Biologiques de Chizé (CEBC-CNRS) Département de Biologie, Université Laval, Québec, QC, Canada
                \textbf{Dominique Berteaux},  Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Chimie et Géographie, Université du Québec à Rimouski, Rimouski, QC, Canada \\

                \subsection*{2. Abstract}
Arctic ecosystems present unique opportunities for community-wide monitoring, in part due to their relatively low species richness. However, conducting research in these remote environments poses significant logistical challenges, resulting in long-term monitoring being exceedingly rare. Here, we focus on the long-term, intensive ecological monitoring efforts conducted on the south plain of Bylot Island (almost 400 km\textsuperscript{2}, Nunavut, Canada), which has generated a remarkable dataset spanning up to 30 years, a rarity in tundra ecosystems. Our goal is to synthesize this dataset and upscale vertebrate abundance data at the landscape level, a prerequisite to conduct community-level analyses. We have standardized data obtained with different field methods to provide readily usable long-term time series of abundance for 35 vertebrate species (30 birds and 5 mammals) present in the study system. Monitoring data includes intensive capture-mark-recapture density estimates of lemmings on trapping grids, systematic or opportunistic nest monitoring conducted across the entire study area or within specific plots for all bird species, transects of vertebrate counts distributed throughout the study area, daily incidental observations of vertebrates and satellite tracking of fox movements. Annual abundance of species was estimated at the landscape level, accounting for spatial variations. Furthermore, we provide body masses for each species, derived from empirical onsite measurements for 18 species and from the literature for the remaining species. Body mass is essential to convert species abundance into biomass for studies of trophic fluxes and ecosystem processes. Our dataset provides a unique opportunity for holistic empirical studies of ecological communities, allowing a deeper understanding of community structure and dynamics. Considering that the study site is a pristine and protected area that has experienced minimal anthropogenic impact, it can also provide an ideal baseline for investigating the impacts of global changes on high-latitude terrestrial ecosystems.
   \section*{D. Key words/phrases}
 Bylot Island, Canadian Arctic, Arctic tundra, 1993-2023, long-term monitoring, biodiversity monitoring, community composition, species abundance, species density, species biomass, species body mass, food web
  \newpage

\section*{\textcolor{Blue}{Class II. Research origin descriptors}}
    \section*{A. Overall project description}
    \subsection*{1. Identity} Understanding the structure and dynamics of Arctic terrestrial communities
        \subsection*{2. Originators}   
        \textbf{Gilles Gauthier}, Centre d’études nordiques, Département de Biologie, Université Laval, Québec, QC, Canada\\
                \textbf{Joël Bêty},  Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la science de la biodiversité du Québec, Département de biologie, chimie et géographie, Université du Québec à Rimouski, Rimouski, QC, Canada \\
                \textbf{Pierre Legagneux}, Chaire de Recherche Sentinelle Nord sur l’impact des migrations animales sur les écosystèmes nordiques, Centre d’Études Nordiques, Centre de la science de la biodiversité du Québec, Centre d’Études Biologiques de Chizé (CEBC-CNRS) Département de Biologie, Université Laval, Québec, QC, Canada
                \textbf{Dominique Berteaux},  Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Chimie et Géographie, Université du Québec à Rimouski, Rimouski, QC, Canada \\

@@

        \subsection*{4. Objectives}
       i) Understand the factors that shape the structure and drive the dynamics of Arctic terrestrial communities.\\
       ii) Predict the effects of environmental changes on the structure and dynamics of Arctic terrestrial communities.

     \subsection*{5. Abstract}
      Arctic terrestrial communities, characterized by relatively low species richness, offer unique opportunities for studying ecological patterns and dynamics in simplified systems. Despite their relative simplicity, these ecosystems feature complex species interactions, extreme seasonal environmental changes, and a significant proportion of migratory species, making it difficult to identify the key factors shaping their structure and dynamics. As global environmental changes accelerate, it is essential to understand the processes driving these communities to eventually predict future impacts on Arctic ecosystems. Our research combines long-term biodiversity monitoring, a community-wide approach, and food web modeling to address these challenges.

      \subsection*{6. Sources of funding}
Natural Sciences and Engineering Research Council of Canada, Fonds Québécois de Recherche Nature et Technologies, Centre d'études nordiques, Natural Resources Canada (Polar Continental Shelf Program), Network of Centers of Excellence Canada (ArcticNet), Canada First Research Excellence Fund (Sentinel North Program), Polar Knowledge Canada, Environment and Climate Change Canada, Canada Foundation for Innovation, Parks Canada Agency, International Polar Year program of the Government of Canada, Crown–Indigenous Relations and Northern Affairs Canada (Northern Contaminant Program), Duck Unlimited Canada, Kenneth M. Molson Foundation (Kenneth M. Molson Foundation’s donation for wildlife research, conservation, and habitat), Garfield Weston Foundation, First Air——Canadian North, Nunavut Wildlife Management Board, Université Laval, Université du Québec à Rimouski
\newpage

@@

                        \subsubsection*{c. Permit history}
All research involving animals on Bylot Island has been approved by an institutional Animal Care Committee. In 1999, the study area became part of Sirmiliik National Park, managed by Parks Canada. Since then, all research activities in the park have been approved by a Joint Park Management Committee.

                \subsubsection*{d. Project personnel}
                \begin{enumerate}[label=\alph*.]
                        \item[] \textit{\textbf{Principal and associated investigators}}\\
                        Gilles Gauthier, Eric Reed, Jean-François Giroux, Dominique Berteaux, Joël Bêty, Josée Lefebvre, Dominique Gravel, Jean-François Therrien, Nicolas Lecomte, Dominique Fauteux, Pierre Legagneux (see \citet{gauthier2024b})
                        \item[] \textit{\textbf{Students}}\\
                        By combining animal and plant ecology, 24 doctoral theses and 56 master theses have been completed in relation to the study area located on the south plain of Bylot Island (see \citet{gauthier2024b}).
                \end{enumerate}
\newpage 
 \section*{\textcolor{Blue}{Class III. Data set status and accessibility}}
    \section*{A. Status}
                \subsection*{1. Latest update} 30th September 2024
        \subsection*{2. Latest archive date} XXXXXX October 2024
        \subsection*{3. Metadata status} XXXXXX October 2024
        \subsection*{4. Data verification} The methods employed to estimate species abundance were subject to several rounds of revision by the authors.
   \section*{B. Accessibility}
                \subsection*{1. Storage location and medium}
The data set is publicly available at \url{https://datadryad.org/XXXXXXXXXXX}.\\[1.5em]
Raw data and codes used to extract the presented data set are publicly available at \url{https://zenodo.org/XXXXXXXX}.

        \subsection*{2. Contact persons}
        \begin{enumerate}[label=\alph*.]
                        \item[] \textit{\textbf{Overall project}}\\
                        Joël Bêty; \textit{\href{mailto:joel_bety@uqar.ca}{joel{\textunderscore}bety@uqar.ca}}; 418 723-1986 \#1701; 300 allée des Ursulines, Rimouski, Québec, Canada, G5L 3A1, Office B-002
                        \item[] \textit{\textbf{Data and codes}}\\
                         Louis Moisan, \textit{\href{mailto:louis.moisan.bio@gmail.com}{louis.moisan.bio@gmail.com}}
                \end{enumerate}
                \subsection*{3. Copyright restrictions}
                None

@@

                        \subsection*{7. Authentication procedures}
                        Sums of the numeric columns: \\
                        b. \texttt{BYLOT-species\_abundance.csv}: abundance= 2293136\\
                        c. \texttt{BYLOT-species\_body\_mass.csv}: body\_mass\_g= 49617; sample\_size= 13902\\
                        d. \texttt{BYLOT-interannual\_variation\_nest\_density.csv}: mean\_nest\_density\_km2= 19.991; sd\_nest\_density\_km2= 10.539; sample\_size\_nest\_density\_km2= 185

@@

 \section*{\textcolor{Blue}{Class V. Supplemental descriptors}}
    \section*{A. Data acquisition}
    		\subsection*{1. Data forms or acquisition methods}
   		See Section \textbf{2. Experimental or sampling design} 
   		\subsection*{2. Location of completed data forms}
        Raw data and codes used to extract the data set and the current document are publicly available at \url{https://zenodo.org/XXXXXXXX}.
        \subsection*{3. Data entry verification procedures}
       	The methods used to extract final species abundance estimates were subject to several rounds of revision by the authors.

@@

    \section*{C. Computer programs and data-processing algorithms}
         \subsection*{1. Program} R version 4.3.2 (2023-10-31)
         \subsection*{2. Operating system} Data preparation was performed on x86\_64-pc-linux-gnu (64-bit) with Ubuntu 22.04.3 LTS.
         \subsection*{3. Packages} dplyr \citep{dplyr}, tidyr \citep{tidyr}, sf \citep{sf}, stringr \citep{stringr}, xtable \citep{xtable}, Distance \citep{miller2019}, ggplot2 \citep{ggplot2}, lme4 \citep{lme4}, AICcmodavg \citep{AICcmodavg}, scales\citep{scales}, ggmap \citep{ggmap}
         \subsection*{4. Codes} Raw data and codes used to extract the presented data set are publicly available at \url{https://zenodo.org/XXXXXXXX}.

    \section*{D. Archiving}
         \subsection*{1. Archival procedures} Data are publicly available at \url{https://datadryad.org/XXXXXXXXXX}.
         \subsection*{2. Redundant archival sites} None

    \section*{E. Publications and results}
The presented estimates of species abundance have not been integrated in publications to date. Previous estimates of species abundance on the souther plain of Bylot Island were presented by \citet{legagneux2012}, however, the temporal series presented here is longer, the methods are more refined and the taxonomic resolution is higher.

>>>>

\begingroup  
  \centering
\textbf{Long-term abundance time-series of the High Arctic terrestrial vertebrate community of Bylot Island, Nunavut}\\[1.5em]
 Louis Moisan\textsuperscript{1,2}, Azenor Bideault\textsuperscript{2,3}, Gilles Gauthier\textsuperscript{4}, Éliane Duchesne\textsuperscript{1}, 
 Dominique Fauteux\textsuperscript{5}, Dominique Berteaux\textsuperscript{1}, Pierre Legagneux\textsuperscript{3,6}, Marie-Christine Cadieux \textsuperscript{3} and Joël Bêty\textsuperscript{1}\\[1.5em]
\textbf{Author Affiliations}:\\
\textsuperscript{1} Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Chimie et Géographie, Université du Québec à Rimouski, Rimouski, QC, Canada\\
\textsuperscript{2} Chaire de Recherche du Canada en Écologie Intégrative, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Université de Sherbrooke, Sherbrooke, QC, Canada\\
\textsuperscript{3} Chaire de Recherche Sentinelle Nord sur l’Impact des Migrations Animales sur les Écosystèmes Nordiques, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Université Laval, Québec, QC, Canada\\
\textsuperscript{4} Centre d’Études Nordiques, Département de Biologie, Université Laval, Québec, QC, Canada\\
\textsuperscript{5} Centre d’Études Nordiques, Centre de Connaissance et d’Exploration de l’Arctique, Musée Canadien de la Nature, Ottawa, ON, Canada\\
\textsuperscript{6} Centre d’Études Biologiques de Chizé (CEBC-CNRS), Université de La Rochelle, France 
\\[1.5em]
\textbf{Corresponding Author}:\\
\textit{\href{mailto:louis.moisan.bio@gmail.com}{louis.moisan.bio@gmail.com}}\\
[1.5em]
\textbf{Open Research statement}:\\
The complete data set is available as Supporting Information at: \url{https://doi.org/10.5061/dryad.44j0zpcnt}. Metadata document, raw data and codes are also available at \url{https://doi.org/10.5061/dryad.44j0zpcnt}.\\
\endgroup
\newpage

@@

    \section*{C. Data set description}
                \subsection*{1. Originators}
                \textbf{Gilles Gauthier}, Centre d’Études Nordiques, Département de Biologie, Université Laval, Québec, QC, Canada\\
                \textbf{Joël Bêty},  Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Chimie et Géographie, Université du Québec à Rimouski, Rimouski, QC, Canada \\
                \textbf{Pierre Legagneux}, Chaire de Recherche Sentinelle Nord sur l’Impact des Migrations Animales sur les Écosystèmes Nordiques, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Centre d’Études Biologiques de Chizé (CEBC-CNRS) Département de Biologie, Université Laval, Québec, QC, Canada\\
                \textbf{Dominique Berteaux},  Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Chimie et Géographie, Université du Québec à Rimouski, Rimouski, QC, Canada \\

                \subsection*{2. Abstract}
Arctic ecosystems present unique opportunities for community-wide monitoring, in part due to their relatively low species richness. However, conducting research in these remote environments poses significant logistical challenges, resulting in long-term monitoring being exceedingly rare. Here, we focus on the long-term, intensive ecological monitoring efforts conducted on the south plain of Bylot Island (almost 400 km\textsuperscript{2}, Nunavut, Canada), which has generated a remarkable dataset spanning up to 30 years, a rarity in tundra ecosystems. Our goal is to synthesize this dataset and upscale vertebrate abundance data at the landscape level, a prerequisite to conduct community-level analyses. We have standardized data obtained with different field methods to provide readily usable long-term time series of abundance for 35 vertebrate species (30 birds and 5 mammals) present in the study system. Monitoring data includes intensive capture-mark-recapture density estimates of lemmings on trapping grids, systematic or opportunistic nest monitoring conducted across the entire study area or within specific plots for all bird species, transects of vertebrate counts distributed throughout the study area, daily incidental observations of vertebrates and satellite tracking of fox movements. Annual abundance of species was estimated at the landscape level, accounting for spatial variations. Furthermore, we provide body masses for each species, derived from empirical onsite measurements for 18 species and from the literature for the remaining species. Body mass is essential to convert species abundance into biomass for studies of trophic fluxes and ecosystem processes. Our dataset provides a unique opportunity for holistic empirical studies of ecological communities, allowing a deeper understanding of community structure and dynamics. Considering that the study site is a pristine and protected area that has experienced minimal anthropogenic impact, it can also provide an ideal baseline for investigating the impacts of global changes on high-latitude terrestrial ecosystems.
   \section*{D. Key words/phrases}
Arctic tundra, Biodiversity monitoring,  Bylot Island, Canadian Arctic, Community composition, Community structure, Food web, Long-term monitoring, Species abundance, Species biomass, Species body mass

\section*{\textcolor{Blue}{Class II. Research origin descriptors}}
    \section*{A. Overall project description}
    \subsection*{1. Identity} Structure and functioning of Arctic terrestrial ecosystems
        \subsection*{2. Originators}   
        \textbf{Gilles Gauthier}, Centre d’études nordiques, Département de Biologie, Université Laval, Québec, QC, Canada\\
                \textbf{Joël Bêty},  Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la science de la biodiversité du Québec, Département de biologie, chimie et géographie, Université du Québec à Rimouski, Rimouski, QC, Canada \\
                \textbf{Pierre Legagneux}, Chaire de Recherche Sentinelle Nord sur l’impact des migrations animales sur les écosystèmes nordiques, Centre d’Études Nordiques, Centre de la science de la biodiversité du Québec, Centre d’Études Biologiques de Chizé (CEBC-CNRS) Département de Biologie, Université Laval, Québec, QC, Canada\\
                \textbf{Dominique Berteaux},  Chaire de Recherche du Canada en Biodiversité Nordique, Centre d’Études Nordiques, Centre de la Science de la Biodiversité du Québec, Département de Biologie, Chimie et Géographie, Université du Québec à Rimouski, Rimouski, QC, Canada \\

@@

        \subsection*{4. Objectives}
       i) Develop models for the Arctic tundra food web that incorporate seasonality, migratory connectivity and interactions with marine and southern ecosystems.\\
       ii) Predict the effects of global changes on Arctic terrestrial food webs.

     \subsection*{5. Abstract}
Arctic terrestrial communities, characterized by relatively low species richness, offer unique opportunities for studying ecological patterns and dynamics in simplified systems. Despite their relative simplicity, these ecosystems feature complex species interactions, extreme seasonal environmental changes, and a significant proportion of migratory species, making it difficult to identify the key factors shaping their structure and functioning. As global environmental changes accelerate, it is essential to understand the interacting processes driving these communities to eventually predict future impacts on Arctic ecosystems. Our research combines long-term biodiversity monitoring, a community-wide approach, and food web modeling to address these challenges.

      \subsection*{6. Sources of funding}
Natural Sciences and Engineering Research Council of Canada, Fonds Québécois de Recherche Nature et Technologies, Centre d'études nordiques, Natural Resources Canada (Polar Continental Shelf Program), Network of Centers of Excellence Canada (ArcticNet), Canada First Research Excellence Fund (Sentinel North Program), Polar Knowledge Canada, Environment and Climate Change Canada, Canada Foundation for Innovation, Parks Canada Agency, International Polar Year program of the Government of Canada, Crown–Indigenous Relations and Northern Affairs Canada (Northern Contaminant Program), Ducks Unlimited Canada, Kenneth M. Molson Foundation (Kenneth M. Molson Foundation’s donation for wildlife research, conservation, and habitat), Garfield Weston Foundation, First Air——Canadian North, Nunavut Wildlife Management Board, Université Laval, Université du Québec à Rimouski
\newpage

@@

                        \subsubsection*{c. Permit history}
All research involving animals on Bylot Island has been approved by an institutional Animal Care Committee. In 1999, the study area became part of Sirmilik National Park, managed by Parks Canada. Since then, all research activities in the park have been approved by a Joint Park Management Committee.

                \subsubsection*{d. Project personnel}
                \begin{enumerate}[label=\alph*.]
                        \item[] \textit{\textbf{Principal and associated investigators}}\\
                        Gilles Gauthier, Austin Reed, Jean-François Giroux, Dominique Berteaux, Joël Bêty, Josée Lefebvre, Dominique Gravel, Jean-François Therrien, Nicolas Lecomte, Dominique Fauteux, Pierre Legagneux (see \citet{gauthier2024b})
                        \item[] \textit{\textbf{Students}}\\
                        By combining animal and plant ecology, 24 doctoral theses and 56 master theses have been completed in relation to the study area located on the south plain of Bylot Island (see \citet{gauthier2024b}).
                \end{enumerate}
\newpage 
 \section*{\textcolor{Blue}{Class III. Data set status and accessibility}}
    \section*{A. Status}
                \subsection*{1. Latest update} 25 October 2024
        \subsection*{2. Latest archive date} 25 October 2024
        \subsection*{3. Metadata status} 25 October 2024
        \subsection*{4. Data verification} The methods employed to estimate species abundance were subject to several rounds of revision by the authors.
   \section*{B. Accessibility}
                \subsection*{1. Storage location and medium}
The complete data set is available as Supporting Information at: \url{https://doi.org/10.5061/dryad.44j0zpcnt}.\\
Metadata document, raw data and codes are also available at \url{https://doi.org/10.5061/dryad.44j0zpcnt}.

        \subsection*{2. Contact persons}
        \begin{enumerate}[label=\alph*.]
                        \item[] \textit{\textbf{Overall project}}\\
                        Joël Bêty; \textit{\href{mailto:joel_bety@uqar.ca}{joel{\textunderscore}bety@uqar.ca}}; 418 723-1986 \#1701; 300 allée des Ursulines, Rimouski, Québec, Canada, G5L 3A1, Office B-002
                        \item[] \textit{\textbf{Specific subproject description}}\\
                         Louis Moisan, \textit{\href{mailto:louis.moisan.bio@gmail.com}{louis.moisan.bio@gmail.com}}
                \end{enumerate}
                \subsection*{3. Copyright restrictions}
                None

@@

                        \subsection*{7. Authentication procedures}
                        Sums of the numeric columns: \\
                        b. \texttt{BYLOT-species\_abundance.csv}: abundance= 2280165\\
                        c. \texttt{BYLOT-species\_body\_mass.csv}: body\_mass\_g= 49617; sample\_size= 13902\\
                        d. \texttt{BYLOT-interannual\_variation\_nest\_density.csv}: mean\_nest\_density\_km2= 19.991; sd\_nest\_density\_km2= 10.539; sample\_size\_nest\_density\_km2= 185

@@

 \section*{\textcolor{Blue}{Class V. Supplemental descriptors}}
    \section*{A. Data acquisition}
    		\subsection*{1. Data forms or acquisition methods}
   		See Section \textbf{2. Experimental or sampling design} 
   		\subsection*{2. Location of completed data forms}
        Raw data and codes used to extract the data set and the current document are publicly available at \url{https://doi.org/10.5061/dryad.44j0zpcnt}.
        \subsection*{3. Data entry verification procedures}
       	The methods used to extract final species abundance estimates were subject to several rounds of revision by the authors.

@@

    \section*{C. Computer programs and data-processing algorithms}
         \subsection*{1. Program} R version 4.3.2 (2023-10-31)
         \subsection*{2. Operating system} Data preparation was performed on x86\_64-pc-linux-gnu (64-bit) with Ubuntu 22.04.3 LTS.
         \subsection*{3. Packages} dplyr \citep{dplyr}, tidyr \citep{tidyr}, sf \citep{sf}, stringr \citep{stringr}, xtable \citep{xtable}, Distance \citep{miller2019}, ggplot2 \citep{ggplot2}, lme4 \citep{lme4}, AICcmodavg \citep{AICcmodavg}, scales\citep{scales}, ggmap \citep{ggmap}
         \subsection*{4. Codes} Raw data and codes used to extract the presented data set are publicly available at \url{https://doi.org/10.5061/dryad.44j0zpcnt}.

    \section*{D. Archiving}
         \subsection*{1. Archival procedures} Data are publicly available at \url{https://doi.org/10.5061/dryad.44j0zpcnt}.
         \subsection*{2. Redundant archival sites} None

    \section*{E. Publications and results}
The presented estimates of species abundance have not been integrated in publications to date. Previous estimates of species abundance on the southern plain of Bylot Island were presented by \citet{legagneux2012}, however, the temporal series presented here is longer, the methods are refined and the taxonomic resolution is higher.

### 2024-10-25 MetadataS1/tables/table_summary_methods_and_abundance.tex
minor change table uncertainty intervals
version submitted to ecology - Data paper

% Thu Oct 10 16:07:59 2024

@@

Snow goose & Intensive study area-wide monitoring based on a combination of methods (transects, point counts and nest monitoring plots) and annual colony outline & high & Multiple independent methods and annual colony outline & 8687* & 49076* & 31852* & 12092 & 12 (2010-2019, 2022-2023) \\ 

>>>>

% Fri Oct 25 14:16:25 2024

@@

Snow goose & Intensive study area-wide monitoring based on a combination of methods (transects, point counts and nest monitoring plots) and annual colony outline & high & Multiple independent methods and annual colony outline & 7982* & 47859* & 30771* & 11962 & 12 (2010-2019, 2022-2023) \\ 
